\documentclass[10pt]{article}

\usepackage{eucommon}
\geometry{a4paper, portrait, margin=30mm}

\setlength\parskip{0.5\baselineskip}

\begin{document}
\thispagestyle{empty}

\section*{EU:tPoP Reference Sheet}

This is a reference sheet for those who want something more verbose than official Player Aid,
but less verbose than Rules.
It includes most of the rules and presents them as bullet points.
It does not include setup rules and some things that are already presented in a concise way
in the Rules (e.g. definitions on pages 3-5).


The content is fitted on 12 A4-size pages which are grouped in 3:
3 pages for Sequence of Play, 3 pages for Actions other than Military Actions,
3 pages for Military Actions, and finally, 3 pages containing Other Rules. In some places, words are abbreviated and articles dropped to save space. Therefore, all statements are not grammatically correct sentences, but hopefully they are still easily understandable.


The pages are meant to be joined to form two 3\texttimes A4-size foldable sheets so that
one of them would contain Sequence of Play and Other Rules on opposite sides,
and the other one would have all the Actions.
There will be a separate file where this info page is omitted and other pages appropriately ordered
for a 2-sided print using a regular office printer.


\subsection*{Formatting}

Main Rules are written in black. These apply to both human players and bots,
unless inapplicable to bots (e.g bots do not deal with \ducats).
\botrule{Bot Rules are written in dark gray. These are relevant only when bots are in play.}
References to specific pages (e.g. \dprime(p.~2)\dprime) also follow the same colors.
They are written in black when they refer to Main Rules and \botrule{in dark gray}
when they refer to Bot Rules.


\end{document}
