\documentclass[10pt]{article}

\usepackage{eucommon}

% Text Columns
\usepackage{flowfram}
\newflowframe[1-3]{\columnwidth}{\textheight}{0mm}{0mm}[leftCol]
\newflowframe[1-2]{\columnwidth}{\textheight}{\middleColX}{0mm}[middleCol]
\newflowframe[1-2]{\columnwidth}{\textheight}{\rightColX}{0mm}[rightCol]

% Define columns that contain only Bot rules separately and set their text color,
% because color defined by \botrules is reset when moving to next frame.
% Using multicols instead of flowfram does not have this problem between columns (it has it on page breaks),
% but multicols makes some spacing larger, so it would be more difficult to fit everything
\newflowframe[3]{\columnwidth}{\textheight}{\middleColX}{0mm}[middleColThirdPage]
\newflowframe[3]{\columnwidth}{\textheight}{\rightColX}{0mm}[rightColThirdPage]
\setflowframe*{middleColThirdPage,rightColThirdPage}{textcolor=botrulescolor}

\begin{document}
\addbackground
\addfooter

\sectionbg{Other Rules}

\subsection*{General Notes \rulesref{(p.~2)}}
\subsubsection*{Token Limits}
\begin{itemize}
	\item Generally limited. If nothing in supply, take from anywhere. Exceptions below
	\item \strong{May not be moved}
	\begin{itemize}
		\item Towns (\town), Vassal tokens (\vassal)
		\item Alliances (\alliance/\activeally), Marriages (\marriage/\disputedsuccession)
		\item Crusade/Excommunicated token
		\item Mercenary Units
		\item Allied Units
		\item Religion tokens in State Religion slot
		\item Ill health tokens (\illhealth) on Characters
		\item \dprime Unlimited\dprime\xspace tokens
	\end{itemize}
	\item \strong{Cubes} (\cube)
	\begin{itemize}
		\item Take from anywhere except
		\item Roma Cardinal
		\item \emph{Changed Nat. Focus} slot
		\item Cubes covering income slots
		\item No more than 10 \monarchpower of any type (p.~3)
	\end{itemize}
	\item \strong{Unlimited}
	\begin{itemize}
		\item Ducats (\ducats)
		\item War/Truce tokens
		\item Occupied tokens
		\item +1\manpower tokens
		\item Tag chits
	\end{itemize}
\end{itemize}

\subsubsection*{Rounding}
\begin{itemize}
	\item Round up unless stated otherwise
\end{itemize}

\subsection*{Governing PR \rulesref{(p.~20-21)}}
\subsubsection*{Stability \rulesref{(p.~20)}}
\begin{itemize}
	\item If gaining \stability and \stability = 3, gain 2\adminpower per step
	\item If losing \stability and \stability = -3, lose 2\adminpower per step
	\begin{itemize}
		\item If <2\adminpower, lose any \monarchpower per missing \adminpower
		\item If no \monarchpower, ignore this penalty
	\end{itemize}
\end{itemize}

\subsubsection*{Bankruptcy \rulesref{(p.~21)}}
\begin{itemize}
	\item When cannot pay a mandatory cost and cannot take a Loan
	\begin{itemize}
		\item Lose 3\stability
		\item Lose \p5
		\item Discard all \ducats and 3\interest from Treasury
		\item Disband all Mercenaries
		\item Fire all Advisors
		\item Lose ½ of \monarchpower per type (max 3 per type)
	\end{itemize}
\end{itemize}

\subsubsection*{Towns \rulesref{(p.~21)}}
\begin{itemize}
	\item If out of Large \towns, use 2 Small \towns instead
	\item If out of Small \towns, use a \vassal instead
\end{itemize}

\subsubsection*{Core Provinces \rulesref{(p.~21)}}
\begin{itemize}
	\item To place a \core, a player needs to Own all Provinces in the Area
	\item \core may not be placed to an Area where all Provinces already that PR's Core Prov.
	\item Placing \core displaces any \core/\dnpr in the Area
	\item \core counts as \claim
\end{itemize}

\subsection*{Dip. Relations \rulesref{(p.~32-33)}}
\subsubsection*{Influence \rulesref{(p.~32)}}
\begin{itemize}
	\item Area may contain max 5 \influence
	\item \influence may not be placed in Areas where all Provinces are owned by PRs
	\item Once all Provinces in an Area are Owned by PRs, all \influence must be removed
	\item No \influence may be placed in Distant Areas
	\item \colonists may be used as \influence for \action{Forge Alliance} and \action{Call to Arms} in any Distant Area
\end{itemize}

\subsubsection*{Marriages \rulesref{(p.~32)}}
\begin{itemize}
	\item Max 3\marriages (\idea{Cabinet} Idea allows 1 more)
	\item May not enter Marriages during Interregn.
	\item \marriage counts as \influence, but cannot be removed and is excluded from Area's 5 \influence limit
	\item When taking an Action that requires to remove \influence, remove 1 fewer \influence if you have 1+ \marriages in the Area
\end{itemize}

\subsubsection*{Alliances \rulesref{(p.~32)}}
\begin{itemize}
	\item Max 3\alliances (\idea{Cabinet} Idea allows 1 more)
	\item NPR may only be Allied to 1 PR
	\item \strong{Active Allies} (p.~33)
	\begin{itemize}
		\item Part of every War you are involved in (or enter into while they are active)
		\item They defend their Areas with ½ of MC
	\end{itemize}
	\item Alliances with \strong{Distant NPRs} (p.~33)
	\begin{itemize}
		\item Use \colonists instead of \influence for sending CtA
		\item They contribute Allied Units as normal (despite double MC for defense)
	\end{itemize}
\end{itemize}

\subsubsection*{Vassals \rulesref{(p.~33)}}
\begin{itemize}
	\item Vassals are a separate category of Realms (not part of Overlord's Realm, not NPR)
	\item Using \action{Subjugate} Action Card
	\begin{itemize}
		\item Target may not be a Distant Realm
		\item \strong{Without \marriage}, your Base Tax must be ≥ 2× target's Base Tax
		\item \strong{With \marriage}, your Base Tax must be > target's Base Tax
		\item Discard \influence from target Realm = target Tax Inc. + Oppon. \influence in target Realm
		\item When \strong{Vassalizing} your Ally
		\begin{itemize}
			\item Remove your \alliance
			\item Place \vassals on their Prov. (2 on Large)
			\item All other PRs must remove their \marriages
		\end{itemize}
		\item When \strong{Annexing}
		\begin{itemize}
			\item Replace \vassals with \towns
			\item Remove any \marriage
		\end{itemize}
		\item If the \strong{target has Vassals}
		\begin{itemize}
			\item You need a \marriage to Vassalize them
			\item If you also discard \influence from target's Vassals equal to their Tax Income
			\begin{itemize}
				\item They also become you Vassals
			\end{itemize}
			\item Otherwise, they become independent and you may
			\begin{itemize}
				\item Place \alliance on their Capital, \conj{or}
				\item Place \claim in one of their Areas
			\end{itemize}
		\end{itemize}
	\end{itemize}
	\item \strong{\guilsinglright Papal States} and \strong{Emp.} cannot be Vassal.
	\item \strong{Vassals in Wars}
	\begin{itemize}
		\item \claim on Vassal counts as \claim on Overlord
		\item Vassals do not defend themselves
		\item Vassals contribute to Overlord's MC, but not NC
		\item Overlord may Recruit Regular Units and Mercenaries in their Vassals' Areas
	\end{itemize}
\end{itemize}

\subsection*{NPRs \rulesref{(p.~35-36)}}
\begin{itemize}
	\item If natural Capital is Owned by another Realm, then pick a new Capital. Priority: 1.~Large Provinces; 2.~\az
	\item NPR's \strong{Vassals}
	\begin{itemize}
		\item Assist in Wars as if part of Overlord
		\item May be ceded in Peace Resolutions
		\item If Overlord does not exist, or PR \vassal was removed, Vassals become independent
	\end{itemize}
\end{itemize}

\subsubsection*{DNPRs \rulesref{(p.~35)}}
\begin{itemize}
	\item When a DNPR's Province is Annexed or Vassalized, keep \dnpr underneath the \town/\vassal 
	\item \dnpr cannot be placed on PR Core Provinces
\end{itemize}

\subsubsection*{+1\manpower tokens \rulesref{(p.~36)}}
\begin{itemize}
	\item Provide +1 MC
	\item Count as +1 Tax Value for the purposes of 
	\begin{itemize}
		\item Resolving Peace
		\item Contribution of Allied Units
		\item Subjugation
	\end{itemize}
	\item Do not affect Sieges
	\item Removed if Prov. is Annex. or Vassalized
\end{itemize}

\subsection*{Rebels \rulesref{(p.~37)}}
\subsubsection*{Rebel Dice}
\begin{itemize}
	\item Roll Area by Area
	\item \rebellion: Rebellion
	\begin{itemize}
		\item If you have Military Units in the Area
		\begin{itemize}
			\item Add \rebels per \rebellion result
			\item Any Battle is triggered after all Rebel Dice rolls have been resolved
		\end{itemize}
		\item Otherwise
		\begin{itemize}
			\item Assign each \rebellion to one of your \unrest
			\item Core Province gets Occupied
			\item Occ. or non-Core Prov. gets Liber.
		\end{itemize}
	\end{itemize}
	\item \losemonarchpower: Lose 1\monarchpower. If unable to, then pay 2\ducats
	\item \exhaustunits: Exhaust 1\manpower. If unable to, pay 2\ducats
	\item \loseducats: Lose 2\ducats
	\item \removeunrest: Remove 1 \unrest
\end{itemize}

\subsubsection*{\botrules Bot rolls \rulesref{(p.~4)}}
{\botrules
\begin{itemize}
	\item Roll for all Areas at once (max 5 dice)
	\item \loseducats \exhaustunits \losemonarchpower: Lose 1 \botpower
	\begin{itemize}
		\item Lose max 1 \botpower, even if more rolled
	\end{itemize}
	\item \removeunrest: Remove 1 \unrest
	\item \rebellion: Rebellion
	\begin{itemize}
		\item If possible, apply in Area with Bot's Army
		\item If Prov. gets Liber., place \claim in the Area
	\end{itemize}
\end{itemize}
}

\subsubsection*{Rebel Units}
\begin{itemize}
	\item \rebels are Hostile to all PRs
	\item \strong{Sieging}
	\begin{itemize}
		\item If Province is Core of its Owner
		\begin{itemize}
			\item Place \rebeltown on top of it
		\end{itemize}
		\item If Occupied \conj{or} not Core of its Owner
		\begin{itemize}
			\item It is Liberated
		\end{itemize}
	\end{itemize}
	\item \strong{Liberation}
	\begin{itemize}
		\item If \strong{Occupied} by an Enemy of Province's Lawful Owner, remove Occupier's \town
		\item If \strong{not a Core Province} of PR who Owns or has Vassalized it
		\begin{itemize}
			\item Remove \town/\vassal
			\item If Core Province of another PR, they place a \town there
		\end{itemize}
		\item If \strong{Territory}, replace \town with a \dnpr (color chosen by the Active Player)
		\item A PR whose Province is Liberated by Rebels must \strong{place a CB} on the new Owner's Capital and remove any Truce
		\item \botrule{Bot \strong{places a \claim} if their Province gets Liberated by Rebels (p.~4)}
	\end{itemize}
	\item \strong{Optional rule 5: Religious Rebels}
	\begin{itemize}
		\item Turn/place all \rebeltowns pentagram side up in Areas with Religious Dissent
		\item If Religious Rebels Occupy your Capit. \conj{and} 2+ other Provinces, you may
		\begin{itemize}
			\item \action{Change State Religion} to the Religion of your Capital Area, \conj{and}
			\item Remove \rebels and \rebeltowns in Areas of your new State Religion
		\end{itemize}
	\end{itemize}
\end{itemize}

\subsection*{Religion, Faith \rulesref{(p.~38)}}
\subsubsection*{Catholicism}
\begin{itemize}
	\item Counter-Reformed Realms and Areas are also considered to be Catholic
	\item Abilities
	\begin{itemize}
		\item Have access to Papal Curia
		\item May \action{Change State Religion} to Protestantism from Age II onwards
	\end{itemize}
\end{itemize}

\subsubsection*{Protestantism abilities}
\begin{itemize}
	\item Discount of 1\adminpower on \action{Convert Area}
	\item Discount of 1\adminpower on \action{Development}
	\item May \action{Change State Rel.} to Catholicism
\end{itemize}

\subsubsection*{Orthodoxy abilities}
\begin{itemize}
	\item Discount of 1\adminpower when \action{Increasing Stab.} from -1 to 0 or from 0 to 1
\end{itemize}

\subsubsection*{Islam abilities}
\begin{itemize}
	\item May replace the default 3 Infantry Dice with 3 Cavalry Dice
\end{itemize}

\subsubsection*{Diverse Faiths}
\begin{itemize}
	\item Means no dominant faith in the Area
	\item Cannot be State Religion
\end{itemize}

\subsubsection*{Revolutionary Ideology}
\begin{itemize}
	\item Token is placed on top of existing Religion (instead of replacing it)
	\item If Revolutionary Realm \action{Researches} Gov. Form other than \idea{Revolutionary Regime}
	\begin{itemize}
		\item They remove \revolution in Capital Area, \conj{and}
		\item Change State Religion to match the Religion of Capital Area
	\end{itemize}
\end{itemize}

\subsection*{Prestige (\prestige) \rulesref{(p.~42-43)}}

\subsubsection*{Missions}
\begin{itemize}
	\item May not be completed in Phase 1
	\item Rewards follow Standard Event Effects
\end{itemize}

\subsubsection*{Milestones}
\begin{itemize}
	\item When completed at same time, then tie breaker is Turn order (starting with Active Player in Phase 2, otherwise with the First Player), unless otherwise stated on the Milestone
\end{itemize}

\subsection*{Papal Curia \rulesref{(p.~45-46)}}
\begin{itemize}
	\item \# of Regular Cardinal Slots = \# of Catholic PRs + 1
	\item \strong{Roma Cardinal} belongs to PR who
	\begin{itemize}
		\item Is Allied to the \guilsinglright Papal States, \conj{or}
		\item Controls Roma
		\begin{itemize}
			\item This supersedes the Alliance
			\item PR may not have other \cardinals
		\end{itemize}
	\end{itemize}
	\item \strong{Papal Controller}
	\begin{itemize}
		\item PR with most \cardinals
		\item The left-most \cardinal breaks ties
		\item Bonuses
		\begin{itemize}
			\item +1\diplopower in Phase 4, Step D
			\item Discount of 1\ducat per Advisor in Phase 4, Step B
			\item Discount of 1\adminpower for all Actions that Increase \stability
			\item Has Access to Papal Actions
		\end{itemize}
	\end{itemize}
	\item \strong{Uncontested Papal Controller}
	\begin{itemize}
		\item PR with most \cardinals, min 2 and no tie
		\item Extra \prestige in Phase 4, Step E
	\end{itemize}
\end{itemize}

\subsection*{HRE \rulesref{(p.~43-45)}}
\subsubsection*{Imperial Authority \normal{(p.~43)}}
\begin{itemize}
	\item Max \authority = \# of Elector Areas + 1
	\item Emperor's bonuses
	\begin{itemize}
		\item Additional \manpower = \authority
		\item Additional Tax Income = \authority
		\item If \authority ≥ 1, may use \emph{Defending the HRE}
		\item If \authority = 2 or 3, then +1\diplopower
		\item If \authority = 4 or 5, then +1\diplopower, +1\milpower
		\item If \authority = 6, then +2\diplopower, +1\milpower, +\p1
	\end{itemize}
	\item Gaining 1 \authority
	\begin{itemize}
		\item \action{Increase Authority}: Pay \adminpower = 1 + current \authority
		\item Win a War vs non-HRE Aggressor (if no HRE Provinces ceded (p.~44))
		\item Reincorporate HRE Area
		\item If \authority~< 3 upon Election
	\end{itemize}
	\item Losing 1 \authority
	\begin{itemize}
		\item Refusing CtA when non-HRE Aggressor Declares War on an Imperial Subject
		\item An Area leaves the HRE
		\item Lose a War vs non-HRE Aggressor
		\item Emperor Declares War on HRE Member without a CB
		\item Emp. enforces Full Annex. on HRE Member with the same State Religion
	\end{itemize}
	\item Lose \authority if max \authority goes below current \authority
\end{itemize}

\subsubsection*{Imperial Influence \rulesref{(p.~44)}}
\begin{itemize}
	\item Works like regular \influence except
	\begin{itemize}
		\item Is placed only in Phase 5, Step B
		\item Must be placed in HRE Areas with at least 1 NPR HRE Member
		\item Removed when Area leaves HRE
		\item May not be used for \action{Subjugate}
	\end{itemize}
\end{itemize}

\subsubsection*{HRE Lands \rulesref{(p.~44)}}
\begin{itemize}
	\item \strong{HRE Members} -- Realms with Capital in HRE (can be PRs, NPRs, Vassal Realms)
	\item \strong{Imperial Subjects} -- HRE Members except the Emperor
	\item \strong{Unlawful Occupant} -- Capital not in HRE but
	\begin{itemize}
		\item Occupies \town in HRE, \conj{or}
		\item Owns \town in HRE, \conj{or}
		\item Has \vassal in HRE
	\end{itemize}
	\item \strong{Elector Area}
	\begin{itemize}
		\item Marked with \authority on the Map
		\item Must have Capital of 1+ HRE Member
	\end{itemize}
\end{itemize}

\subsubsection*{PR as Imperial Subject \rulesref{(p.~44)}}
\begin{itemize}
	\item May leave HRE only by Mission or Event
\end{itemize}

\subsubsection*{Leaving and Rejoining HRE \rulesref{(p.~45)}}
\begin{itemize}
	\item When all Provinces in an HRE Area are Owned by external Realms except Emp.
	\begin{itemize}
		\item The Area leaves the HRE (place \nothre)
		\item Lose 1\authority
	\end{itemize}
	\item If all HRE Prov. in an Area are Owned or Vassal. by HRE Members or Emperor
	\begin{itemize}
		\item The Area is reincorporated (remove \nothre)
		\item Gain 1\authority
	\end{itemize}
\end{itemize}

\subsubsection*{HRE Religion \rulesref{(adv. rules) (p.~45)}}
\begin{itemize}
	\item Emp. may \action{Change State Rel.} only when HRE Rel. is different from Emp.'s Rel.
	\item If Emperor adopts Revolutionary Ideology, then HRE is permanently dissolved
\end{itemize}

\subsubsection*{NPR Emperor \rulesref{(p.~45)}}
\begin{itemize}
	\item Changes in \authority
	\begin{itemize}
		\item When Area leaves the HRE, lose 1\authority
		\item When Area rejoins, gain 1\authority
		\item Based on a die-roll at the end of Round
	\end{itemize}
	%\framebreak
	\item Number of Units defending an HRE Area
	\begin{itemize}
		\item MC of Defending NPRs (as normal)
		\item +3 × \authority
		\item -2 × number of HRE Areas with non-HRE Units prior to this Turn
	\end{itemize}
	\item Emperor cannot be Vassalized
	\item If Emp. is Fully Annexed, HRE dissolves
\end{itemize}

\subsubsection*{Imperial Elections \rulesref{(adv. rules) (p.~45)}}
\begin{itemize}
	\item Not used when Emp. is NPR \botrule{or Bot (p.~6)}
	\item Triggered when
	\begin{itemize}
		\item \authority ≤ 4, \conj{and}
		\item Emp.'s Ruler is replaced/discarded
	\end{itemize}
	\item Eligible \strong{candidate Realm}
	\begin{itemize}
		\item Must be a PR
		\item Must follow official HRE Rel. (if any)
		\item May be non-HRE Realm
		\item May have Interregnum
	\end{itemize}
	\item If there are \strong{no eligible candidates}
	\begin{itemize}
		\item The current Emperor retains the title
		\item \authority drops by 2
	\end{itemize}
	\item \strong{Elector Areas vote} for candidates
	\begin{itemize}
		\item Elec. Area votes for candidate that has most \influence (incl. Imp. \influence) in that Area
		\item Elec. Area with no NPR Prov. where all \vassals belong to the same PR
		\begin{itemize}
			\item Votes for that PR, if eligible
		\end{itemize}
		\item If PR has Capital in an Elector Area
		\begin{itemize}
			\item If eligible, that PR gets the vote
			\item If not, the Area does not vote
		\end{itemize}
		\item All ties are decided by current Emp.
	\end{itemize}
	\item If \authority < 3 following election of a new Emp.
	\begin{itemize}
		\item \authority increases by 1
	\end{itemize}
	\item If new PR is elected and \emph{Defending the HRE} is active
	\begin{itemize}
		\item New Emp. may place CB on any non-HRE Realm at War with NPR HRE Members
		\item Imperial \manpower stays the same and can be used as normal by the new Emperor
	\end{itemize}
\end{itemize}


\botrules % Applies only until the end of column
\sectionbgbot{Bot Rules}
\subsectionbot{Choice Proc. \botrulesref{(p.~3)}}

\subsubsection*{At War?}
\begin{itemize}
	\item If no Enemy has Provinces remaining, consider the Bot not at War for all choices
\end{itemize}

\subsubsection*{Realm Selection}
\begin{itemize}
	\item Use Targeting Charts
	\item Priorities for picking a Realm in an Area
	\begin{enumerate}
		\item Capital in the Area
		\item Highest tot. Tax Val. Owned in Area
		\item Random
	\end{enumerate}
\end{itemize}

\subsubsection*{Province, Area, Sea Zone Selection}
\begin{itemize}
	\item When applying effects beneficial to them or bad for an Opponent
	\begin{itemize}
		\item Prioritize highest Tax Value
	\end{itemize}
	\item When applying effects bad for them or beneficial to an Opponent
	\begin{itemize}
		\item Prioritize lowest Tax Value
	\end{itemize}
	\item Otherwise, \az
\end{itemize}

\subsubsection*{Opponent Selection}
\begin{enumerate}
	\item Opponent at War with Bot (if applicable)
	\item Roll a die
	\begin{itemize}
		\item 1-3: Highest \prestige
		\item 4-6: Highest Tax Income
	\end{itemize}
	\item Human players before Bots
	\item Random	
\end{enumerate}

\subsectionbot{Ideas \botrulesref{(p.~3)}}
\begin{itemize}
	\item Bots do not take Idea effects into account
\end{itemize}

\subsectionbot{Token Limits \botrulesref{(p.~4)}}
\subsubsection*{Cubes}
\begin{itemize}
	\item If out of \cubes, take according to the following priority
	\begin{enumerate}
		\item Take \cubes from Spent \botpower
		\item Take \influence from Areas w/o Bot's \alliance/\marriage (prefer furthest from Bot's Cap. Area)
		\item Take from Areas of an Ally with the lowest Tax Income
		\item Take from Available \botpower
	\end{enumerate}
\end{itemize}

\subsubsection*{Towns}
\begin{itemize}
	\item If out of \towns, the Bot will not Siege Provinces or Colonize Territories
\end{itemize}

\subsubsection*{Claims \& Core Tokens}
\begin{itemize}
	\item Max 6 \claims (numbered 1-6)
	\item Max 2 \cores (numbered 7-8)
	\item If out of \claims, take according to the following priority
	\begin{enumerate}
		\item Take non-Colonial Distant \claims
		\item Take \claims from a Main Map Area with the lowest Tax Value
	\end{enumerate}
	\begin{itemize}
		\item Tie breakers
		\begin{enumerate}
			\item Furthest from the Capital Area
			\item \az
		\end{enumerate}
	\end{itemize}
\end{itemize}

\subsubsection*{Other Limited Tokens}
\begin{itemize}
	\item Avoid removing directly beneficial
	\item Prefer removing directly harmful
	\item Otherwise \az
\end{itemize}

\subsectionbot{Bots \& Alliances \botrulesref{(p.~4)}}
\begin{itemize}
	\item Bots never enter into Alliances with Opponents (unless through an Event)
\end{itemize}

\subsectionbot{Covert Actions \botrulesref{(p.~4)}}
\begin{itemize}
	\item PRs counter Bot's Cov. Act. as normal
	\item Bots never counter Covert Actions 
\end{itemize}

\subsectionbot{Bot Warfare \botrulesref{(p.~5)}}
\begin{itemize}
	\item When recruiting, Bots always pay full \botpower price, even if less Available \manpower
\end{itemize}

\subsubsection*{Maximum Army Capacity (MAC)}
\begin{itemize}
	\item Area with land connection to Capital (continuous chain of Bot's \towns that are Adjacent by Land) -- unlimited
	\item Otherwise -- Bot's MC for the Area + 3 (min 9, if Naval Bridge closes the only gap in land connection to the Capital)
	\item When \emph{Defending the HRE} is active (p.~6)
	\begin{itemize}
		\item Treat all HRE Areas as connected to Emperor's Capital for MAC purposes
	\end{itemize}
\end{itemize}

\subsubsection*{Movement}
\begin{itemize}
	\item Normally up to 2 spaces and stops when entering Hostile or Neutral Area
	\item Bot's \strong{Naval Bridge} can be crossed by up to 9 Units, excess Units are laid down
	\item Bots ignore \strong{Mountain Borders}
	\item Moving into Neutral Areas
	\begin{itemize}
		\item Remove 1 \influence if any
		\item Not allowed if Bot's \claim in the Area
	\end{itemize}
\end{itemize}

\subsubsection*{Ship placement}
\begin{itemize}
	\item Never on Trade Protection slots
	\item Adjacent to own Ports or Ships
\end{itemize}

\subsectionbot{Targeting Charts \botrulesref{(p.~6)}}
\begin{itemize}
	\item \strong{Target types}
	\begin{itemize}
		\item Realms
		\item \dprime Owner of [Province]\dprime
		\begin{itemize}
			\item Lawful Owner if Occupied
		\end{itemize}
		\item \dprime Realm in Area\dprime, preference:
		\begin{enumerate}
			\item Valid Realm with Capit. in the Area
			\item Valid Realm with Highest Tax Value Owned in the Area
			\item \az
		\end{enumerate}
	\end{itemize}
	\item If \strong{mil. target is NPR}, place \claim. Priority:
	\begin{enumerate}
		\item In named Area or Area of named Prov.
		\item In target's Capital Area
	\end{enumerate}
	\item \strong{Vacant Territory} as target
	\begin{itemize}
		\item If Bot has \idea{QftNW}, place \claim, end Turn
		\item Otherwise, invalid target
	\end{itemize}
	\item \strong{Invalid military targets}
	\begin{itemize}
		\item Vassal ^^^^2192 Substitute: Overlord
		\item All target's Prov. Owned by PRs or DNPRs ^^^^2192 Substitute: Owner of target's Capital
		\item Bot's Ally
		\item Truce with the Bot
		\item Opponent who has Passed, including their NPR Allies and HRE Subjects 
		\item Bot has 4+ \influence in target's Areas
		\item All target's Prov. already owned by Bot
	\end{itemize}
	\item \strong{Invalid diplomatic targets}
	\begin{itemize}
		\item Opponent
		\item At War with the Bot
		\item DNPR with 10+ Tax Income
		\item All target's Prov. Owned by PRs or DNPRs
	\end{itemize}
\end{itemize}


\end{document}
