\documentclass[10pt]{article}

\usepackage{eucommon}

% Define frame heights and widths
\newlength{\fhPeaceSeq} \setlength\fhPeaceSeq{23.5\baselineskip}
\newlength{\fhNprInvasions} \setlength\fhNprInvasions{29.5\baselineskip}
\newlength{\fhFirstPageLong} \setlength\fhFirstPageLong{\calc{\textheight - \fhPeaceSeq - \frameToTextSpacing}}
\newlength{\fhFirstPageShort} \setlength\fhFirstPageShort{\calc{\textheight - \fhPeaceSeq - \fhNprInvasions - \frameToFrameSpacing}}

\newlength{\fhPeaceTerms} \setlength\fhPeaceTerms{45.5\baselineskip}
\newlength{\fhSecondPage} \setlength\fhSecondPage{\calc{\textheight - \fhPeaceTerms - \frameToTextSpacing}}

\newlength{\fhManpower} \setlength\fhManpower{9\baselineskip}
\newlength{\fhImpInfluence} \setlength\fhImpInfluence{10\baselineskip}
\newlength{\fhHreReligion} \setlength\fhHreReligion{10\baselineskip}
\newlength{\fhBotDeck} \setlength\fhBotDeck{5\baselineskip}
\newlength{\fhCrusade} \setlength\fhCrusade{9\baselineskip}
\newlength{\fhPowerStruggle} \setlength\fhPowerStruggle{9\baselineskip}
\newlength{\frameManpowerY} \setlength\frameManpowerY{\calc{\textheight - \fhManpower}}
\newlength{\frameImpInfluenceY} \setlength{\frameImpInfluenceY}{\calc{\frameManpowerY - \fhImpInfluence - \frameToFrameSpacing}}
\newlength{\frameHreReligionY} \setlength{\frameHreReligionY}{\calc{\frameImpInfluenceY - \fhHreReligion - \frameToFrameSpacing}}
\newlength{\frameBotDeckY} \setlength{\frameBotDeckY}{\calc{\frameHreReligionY - \fhBotDeck - \frameToFrameSpacing}}
\newlength{\frameCrusadeY} \setlength{\frameCrusadeY}{\calc{\frameBotDeckY - \fhCrusade - \frameToFrameSpacing}}
\newlength{\framePowerStruggleY} \setlength{\framePowerStruggleY}{\calc{\frameCrusadeY - \fhPowerStruggle - \frameToFrameSpacing}}

% Text Columns
\usepackage{flowfram}
\newflowframe[1]{\columnwidth}{\fhFirstPageShort}{0mm}{\calc{\textheight - \fhFirstPageShort}}[firstPageLeftCol]
\newflowframe[1]{\columnwidth}{\fhFirstPageLong}{\middleColX}{\calc{\fhPeaceSeq + \frameToTextSpacing}}[firstPageMiddleCol]
\newflowframe[1]{\columnwidth}{\fhFirstPageLong}{\rightColX}{\calc{\textheight - \fhFirstPageLong}}[firstPageRightCol]
\newflowframe[2]{\columnwidth}{\fhSecondPage}{0mm}{\calc{\textheight - \fhSecondPage}}[secondPageLeftCol]
\newflowframe[2]{\columnwidth}{\fhSecondPage}{\middleColX}{\calc{\textheight - \fhSecondPage}}[secondPageMiddleCol]
\newflowframe[2]{\columnwidth}{\fhSecondPage}{\rightColX}{\calc{\textheight - \fhSecondPage}}[secondPageRightCol]
\newflowframe[3]{\columnwidth}{\textheight}{0mm}{0mm}[leftColFullHeight]
\newflowframe[3]{\columnwidth}{\textheight}{\rightColX}{0mm}[rightColFullHeight]

% Text Frames
\newdynamicframe[1]{\textwidth}{\fhPeaceSeq}{0mm}{0mm}[framePeaceSeq]
\newdynamicframe[1]{\columnwidth}{\fhNprInvasions}{0mm}{\calc{\fhPeaceSeq + \frameToFrameSpacing}}[frameNprInvasions]

\newdynamicframe[2]{\textwidth}{\fhPeaceTerms}{0mm}{0mm}[framePeaceTerms]

\newdynamicframe[3]{\columnwidth}{\fhManpower}{\middleColX}{\frameManpowerY}[frameManpower]
\newdynamicframe[3]{\columnwidth}{\fhImpInfluence}{\middleColX}{\frameImpInfluenceY}[frameImpInfluence]
\newdynamicframe[3]{\columnwidth}{\fhHreReligion}{\middleColX}{\frameHreReligionY}[frameHreReligion]
\newdynamicframe[3]{\columnwidth}{\fhBotDeck}{\middleColX}{\frameBotDeckY}[frameBotDeck]
\newdynamicframe[3]{\columnwidth}{\fhCrusade}{\middleColX}{\frameCrusadeY}[frameCrusade]
\newdynamicframe[3]{\columnwidth}{\fhPowerStruggle}{\middleColX}{\framePowerStruggleY}[framePowerStruggle]

% Arrows
\newdynamicframe[1]{\textwidth}{\textheight}{\pagemarginleft}{-\pagemarginbottom}[frameArrowsPageOne]
\newdynamicframe[2]{\textwidth}{\textheight}{\pagemarginleft}{-\pagemarginbottom}[frameArrowsPageTwo]
\newdynamicframe[3]{\textwidth}{\textheight}{\pagemarginleft}{-\pagemarginbottom}[frameArrowsPageThree]

% Table colors
\usepackage{colortbl}
\usepackage{xcolor}
\ifrenderbw
	\definecolor{tblbgTax}{RGB}{255,255,255}
	\definecolor{tblbgCost}{RGB}{255,255,255}
	\definecolor{tblbgStab}{RGB}{255,255,255}
	\definecolor{tblbgExtra}{RGB}{255,255,255}
\else
	\definecolor{tblbgTax}{RGB}{192,228,174}
	\definecolor{tblbgCost}{RGB}{237,169,150}
	\definecolor{tblbgStab}{RGB}{253,223,130}
	\definecolor{tblbgExtra}{RGB}{138,213,151}
\fi

\begin{document}
\addbackground
\addfooter

\begin{dynamiccontents*}{frameNprInvasions}\begin{eubox}{\fhNprInvasions}
	\subsubsection*{NPR Invasions \normal{(p.~36)}\zsavepos{arrowNprInvasionsEnd}}
	\begin{itemize}
		\item Resolve NPRs in alphabetical order
		\item \strong{Invasion takes place if}
		\begin{itemize}
			\item The NPR is not an Active Ally, \conj{and}
			\item There are no Hostile Units in Areas where the NPR Controls Prov., \conj{and}
			\item There is at least one eligible target Area Adjacent to the NPR
		\end{itemize}
		\item An \strong{Area is eligible if}
		\begin{itemize}
			\item It contains Hostile \towns/\vassals, \conj{and}
			\item If Adj. by Sea only, a connecting Sea Zone contains no Hostile Ships, \conj{and}
			\item It contains no non-Hostile PR Units
		\end{itemize}
	\end{itemize}
	\subsubsection*{Invasion sequence}
	\begin{itemize}
		\item Pick an eligible Area. Priority:
		\begin{enumerate}
			\item NPR's Capital Area
			\item Area with the most NPR's Core Prov.
			\item Area Adjacent by Land
			\item Random
		\end{enumerate}
		\item Add \unrest to 2 Enemy \towns/\vassals in the target Area (pick \az)
		\item Place NPR Units equal to ½ of Tax Value currently Controlled by the NPR (including Vassals)
		\item NPRs invade at normal strength even if not enough tokens in Supply (p.~2)
		\item Resolve Battle immediately (if any)
		\begin{itemize}
			\botrule{\item Place Bot Army in Area (p.~2)}
		\end{itemize}
		\item Leave the NPR Units on board as \rebels
	\end{itemize}
\end{eubox}\end{dynamiccontents*}

\begin{dynamiccontents*}{framePeaceSeq}\begin{eubox}{\fhPeaceSeq}
	\begin{multicols}{3}
		\subsubsection*{Peace Resolution \normal{(p.~29-30)}\zsavepos{arrowPeaceSeqEnd}}
		\begin{itemize}
			\item While \strong{Def. the HRE} is active (p.~44)
			\begin{itemize}
				\item PRs at War with Emperor may enforce Peace on Imp. Subjects only if Victory over Emp. is achieved
				\item Emp. negotiates on behalf of NPR Imperial Subjects as for Active Allies
			\end{itemize}
			\item Peace is resolved with 1 Enemy at a time, except Active Allies, in any order
			\item Treat Vassals as part of their Overlord
			\item In each step, resolve Peace in Turn order
			\item Victory is only assigned to PR
			\begin{itemize}
				\item Who achieved Total/Partial Victory, \conj{or}
				\item Whose Enemy Surrendered, \conj{or}
				\item If agreed as such in Negotiated Peace
			\end{itemize}
			\botrule{\item Bots use the Peace Resolution chart (p.~15)}
		\end{itemize}

		\subsubsection*{1. Automatic White Peace}
		\begin{itemize}
			\item Must be resolved
			\item \strong{Requirements}
			\begin{itemize}
				\item Neither side Occupies any Enemy Prov. (incl. Vassals and Active Allies)
			\end{itemize}
		\end{itemize}

		\subsubsection*{2. Total Victory}
		\begin{itemize}
			\item Must be resolved
			\item Treat Active Allies separately
			\item If Peace is made with an \strong{Active Ally}, the Allied PR must remove
			\begin{itemize}
				\item \alliance with that NPR, \conj{and}
				\item Allied Units = ½ of pre-War Tax Income of the NPR
			\end{itemize}
			\item \strong{Requirements}
			\begin{itemize}
				\item Occ. all single Enemy's \emph{de jure} Prov.
				\item Enemy has no Deployed Land Units
			\end{itemize}
		\end{itemize}

		\subsubsection*{3. Partial Victory or Inconclusive}
		\begin{itemize}
			\item May decide not to resolve
			\item If Enemy \strong{Surrenders}
			\begin{itemize}
				\item Gain \p2, Enemy loses \p2
				\item May enforce Peace as if Part. Victory
				\item War must end this Round
			\end{itemize}
			\item \strong{Optional Rule 3: No Surrender}
			\item \strong{Partial Victory requirements}
			\begin{itemize}
				\item If Enemy is a PR, your Deployed Land Units must outnumber Enemy 2:1
				\item If Enemy is NPR or Bot, your Depl. Land Units must outnum. \rebels in your Areas plus Enemy Depl. Land Units
				\item Units on Dist. Continents where the other Realm has no \towns do no count
			\end{itemize}
			\item If PR Enemy has \strong{Active Allies}
			\begin{itemize}
				\item If and only if achieved against PR, then achieved against their Active Allies
				\item Only a single Peace Term may be chosen for the PR and their Act. Allies
			\end{itemize}
			\item If \strong{inconclusive}
			\begin{itemize}
				\item NPR accepts White Peace
				\item Bot accepts White Peace if Tax Value of their \towns Occupied by you > your \towns Occupied by them
			\end{itemize}
		\end{itemize}

		\subsubsection*{4. Aftermath}
		\begin{itemize}
			\item PRs at Peace must move Units to the nearest Friendly Area (count 1 for each Area/Sea Zone)
			\begin{itemize}
				\item If equally close, then PR may choose
				\item This movement has no cost
			\end{itemize}
			\item PRs at Peace flip their \activeallies back to \alliance
			\item PRs at Peace remove Allied Units
			{\botrules
			\item If a Bot is now at Peace (p.~2-3)
			\begin{itemize}
				\item Remove Bot's Army, unless Bot's \towns in the Area have \unrest or \rebeltown
			\end{itemize}
			\item Replace Fully Annexed Bots (p.~3,~6)
			}
		\end{itemize}
	\end{multicols}
\end{eubox}\end{dynamiccontents*}

\sectionbg{Sequence \normal{\Large{(p.~8-11)}}}
\framebreak % Hack: without manual frame break subsection heading is not red
\subsection*{1. Draw Cards}
\begin{itemize}
	\item May not score Missions in Phase 1 (p.~42)
\end{itemize}
\subsubsection*{A. Reveal Events}
\begin{itemize}
	\item Draw \# of PRs + 1, reveal 3 of them
\end{itemize}
\smallheading{Optional Rule 7: Revealing More \normal{(p.~39)}}
\begin{itemize}
	\item If 6 PRs, reveal 4 Events
\end{itemize}
\subsubsection*{B. Draw Action Cards}

\begin{itemize}
	\item Draw 3 cards (may draw one by one)
\end{itemize}

\subsubsection*{C. Pay for Action Cards}
\begin{itemize}
	\item 2 \ducats per drawn card you keep
\end{itemize}

\subsubsection*{D. Pick/Replace Missions}
\begin{itemize}
	\item Mission can be picked if 1+ prerequisite Missions are completed (p.~42)
	\item Max 2 in hand
\end{itemize}

\subsection*{2. Actions}
\begin{itemize}
	\item On each Turn, must take 1 Action, \conj{and}
	\item May take any \# of Minor Actions
	\botrule{\item Bots use Main Turn Structure (p.~7)}
\end{itemize}
\subsubsection*{Passing}
\begin{itemize}
	\item Allowed only if \action{Event} taken
	\item May take Minor Actions on same Turn
	\item First 2/3/3/4 PRs to Pass gain \ducats
	\item If no more PRs eligible to gain \ducats,\\ \strong{End of Action Phase} is triggered
	\begin{itemize}
		\item Each remaining PR may take 1 more Action of their choice, \conj{then}
		\item PRs who still have not taken \action{Event},\\ get one more Turn to take \action{Event}
		\item If PR has taken their final Turn, they are considered to have Passed
	\end{itemize}
\end{itemize}

\subsection*{3. Peace \& Rebels}
\subsubsection*{A. Remove Casus Belli \& Truces}
\begin{itemize}
	\item Lose \p2 if not at war with the CB target
\end{itemize}

\subsubsection*{B. NPR Invasions \normal{(advanced rules)}}
\begin{itemize}
	\item \hspacezero\zsavepos{arrowNprInvasionsStart}NPRs at War might invade PRs
	\botrules
	\item Bots suffer max 1 NPR invasion. Priority: 1. most NPR Units; 2. \az (p.~2)
\end{itemize}

\subsubsection*{C. Rebels Siege or Move}
\begin{itemize}
	\item Resolve by Area: 1. most \rebels; 2. \az
	\item In \strong{Areas with \unrest}, Rebels Siege \unrest. Priority:
	\begin{enumerate}
		\item Large Provinces
		\item If 2+ PRs with \unrest in the Area, PR with lowest Tax Income (no tie) in the Area chooses (p.~37)
		\item \az
	\end{enumerate}
	\item In \strong{Areas with no \unrest}
	\begin{itemize}
		\item If an Area with \unrest is Adj. by Land \conj{and} \rebels will not be outnum. there by PRs
		\begin{itemize}
			\item Move all but 1 \rebel. Priority:\\ 1. most \unrest; 2. most PR \towns; 3. \az
			\item Resolve Battle immediately
		\end{itemize}
		\item Otherwise remove 1\rebel
	\end{itemize}
\end{itemize}

\subsubsection*{\zsavepos{arrowPeaceSeqStart}D. Peace Resolutions\zsavepos{arrowPeaceTermsStart}}
\begin{itemize}
	\item When Emperor makes Peace with an External Aggressor (p.~44-45)
	\begin{itemize}
		\item If Emp. won \conj{and} no HRE Prov. is ceded, raise \authority by 1
		\item If Emp. lost, drop \authority by 1
	\end{itemize}
	\item Raise/drop \authority by \# of Areas joining/leaving HRE (p.~45)
	\item Making Peace flips respective War token(s)
\end{itemize}

\begin{dynamiccontents*}{frameArrowsPageOne}
	% Must be before the page ends but after all \zsavepos in other dynamic frames
	\begin{tikzpicture}
	\useasboundingbox (0,0) rectangle (\paperwidth,\paperheight);

	% Peace Resolution arrows (continues in next page)
	\newlength{\peaceTermsStartY} \setlength{\peaceTermsStartY}{\calc{\zposy{arrowPeaceTermsStart}sp + \arrowAdjustYAfterSubsub}}
	\newlength{\peaceTermsStartX} \setlength{\peaceTermsStartX}{\calc{\zposx{arrowPeaceTermsStart}sp + \arrowToTextSpacing}}
	\newlength{\peaceSeqStartY} \setlength{\peaceSeqStartY}{\calc{\zposy{arrowPeaceSeqStart}sp + \arrowAdjustYBeforeSubsub - 5pt}}
	\newlength{\peaceSeqStartX} \setlength{\peaceSeqStartX}{\zposx{arrowPeaceSeqStart}sp}
	\newlength{\peaceSeqEndY} \setlength{\peaceSeqEndY}{\calc{\zposy{arrowPeaceSeqEnd}sp + \arrowAdjustYAfterSubsub}}
	\newlength{\peaceSeqEndX} \setlength{\peaceSeqEndX}{\calc{\zposx{arrowPeaceSeqEnd}sp + \arrowToTextSpacing}}
	\newlength{\peaceSeqTurnX} \setlength{\peaceSeqTurnX}{\arrowXVerticalMidRight}
	\newlength{\peaceSeqTurnY} \setlength{\peaceSeqTurnY}{\calc{\margin + \fhPeaceSeq + .5\columnsep}}
	\newlength{\peaceSeqTurnXTwo} \setlength{\peaceSeqTurnXTwo}{\calc{\arrowXVerticalLeft + \middleColX}}

	\drawArrow{(\peaceSeqStartX,\peaceSeqStartY) -- (\peaceSeqTurnX,\peaceSeqStartY) -- (\peaceSeqTurnX,\peaceSeqTurnY) -- (\peaceSeqTurnXTwo,\peaceSeqTurnY) -- (\peaceSeqTurnXTwo,\peaceSeqEndY) -- (\peaceSeqEndX,\peaceSeqEndY)}
	\drawLine{(\peaceTermsStartX,\peaceTermsStartY) -- (\pagewidth,\peaceTermsStartY)}

	% NPR Invasions arrow
	\newlength{\nprStartY} \setlength{\nprStartY}{\calc{\zposy{arrowNprInvasionsStart}sp + \arrowAdjustYList}}
	\newlength{\nprStartX} \setlength{\nprStartX}{\calc{\zposx{arrowNprInvasionsStart}sp + \arrowAdjustXBeforeList}}
	\newlength{\nprEndY} \setlength{\nprEndY}{\calc{\zposy{arrowNprInvasionsEnd}sp + \arrowAdjustYAfterSubsub}}
	\newlength{\nprEndX} \setlength{\nprEndX}{\calc{\zposx{arrowNprInvasionsEnd}sp + \arrowToTextSpacing}}
	\newlength{\nprTurnX} \setlength{\nprTurnX}{\arrowXVerticalMidRight}
	\newlength{\nprTurnY} \setlength{\nprTurnY}{\calc{\margin + \textheight + .5\columnsep}}
	\newlength{\nprTurnXTwo} \setlength{\nprTurnXTwo}{\calc{\arrowXVerticalLeft + \middleColX}}

	\drawArrow{(\nprStartX, \nprStartY) -- (\nprTurnX,\nprStartY) -- (\nprTurnX,\nprTurnY) -- (\nprTurnXTwo,\nprTurnY) -- (\nprTurnXTwo,\nprEndY) -- (\nprEndX,\nprEndY)}

\end{tikzpicture}
\end{dynamiccontents*}

\framebreak

\subsubsection*{E. Prestige Penalties}
\begin{itemize}
	\item Flip all \disputedsuccession back to \marriage
	\begin{itemize}
		\item Lose \p3 for each unless
		\begin{itemize}
			\item Only you have \alliance with them, \conj{and}
			\item If it is an NPR, you have the most \influence (min 2) in that Realm
		\end{itemize}
	\end{itemize}
	\item Lose \prestige = Tax Val. of Occup. \towns (max 5)
\end{itemize}

\subsubsection*{F. Interregnums}
\begin{itemize}
	\item Lose 1\stability
	\item Flip \marriages on your Realm
\end{itemize}

\subsubsection*{G. Religious Dissent}
\begin{itemize}
	\item In Areas following a different Religion from your State Religion
	\begin{itemize}
		\item In \conj{each} Area containing your \towns
		\begin{itemize}
			\item Add 1\unrest to any \town of yours
		\end{itemize}
		\item In \conj{1} Area containing your \vassals
		\begin{itemize}
			\item Add 1\unrest to any \vassal of yours, \conj{or}
			\item Remove 1\influence
		\end{itemize}
	\end{itemize}
	\item \botrule{Bots gain max 1 \unrest (p.~3)}
\end{itemize}

\subsubsection*{H. Gain/Remove Unrest}
\begin{itemize}
	\item If at War, add 2 \unrest to your \towns
	\item If ≤ -2\stability, add 1 \unrest to your \towns
	\item If ≥ +2\stability, remove 1 \unrest from your \towns
	\item \botrule{Bots with Adm. Ideas remove 1‑2\unrest (p.~3)}
\end{itemize}

\subsubsection*{I. Roll Rebel Dice}
\begin{itemize}
	\item In turn order, each PR rolls Rebel Dice
\end{itemize}

\begin{dynamiccontents*}{framePeaceTerms}\begin{eubox}{\fhPeaceTerms}
	\begin{multicols}{3}
		\subsubsection*{\zsavepos{arrowPeaceTermsEnd}Peace Terms \normal{(p.~30-31)}}
		\begin{itemize}
			\item One Peace term per War/Enemy
			\item Any gained \influence may displace other \influence if the Area is full
		\end{itemize}

		\subsubsection*{White Peace}
		\begin{itemize}
			{
				\color{peaceReqColor}
				\item \strong{Requirements}
				\begin{itemize}
					\item Total Victory to Enforce
				\end{itemize}
			}
			\item All Occupied Provinces must be returned to their Lawful Owners
			\item All involved PRs lose \p1
		\end{itemize}

		\subsubsection*{Keep Current Board State}
		\begin{itemize}
			{
				\color{peaceReqColor}
				\item \strong{Requirements}
				\begin{itemize}
					\item Partial or Total Victory to Enforce
				\end{itemize}
			}
			\item Occupied Capitals must be returned
			\begin{itemize}
				\item 10\ducats ransom to the Occupier
			\end{itemize}
			\item By default both sides keep all non-Capital Provinces that they Occupy
			\item Victor, instead of keeping them, may
			\begin{itemize}
				\item Exchange them for Prov. of equal Tax Val. that the Loser Occupies
				\item Return them for 3\ducats per Tax Value
				\item Liberate them, except Loser's Core Prov. and their Active Ally's Prov.
				\begin{itemize}
					\item Score \p1 per Tax Value Liberated
					\item May gain \alliance with 1 Liber. NPR
					\item Place 2 \influence in that NPR's Areas
				\end{itemize}
			\end{itemize}
			\item Max \ducats demanded is 2× Tax Income of the Loser (after return of the Provinces)
			\item PRs may discard \claim from Area(s) of gained Prov. to remove 2 \unrest from same Area(s)
			\item PRs may place \claim in each Area where they lost 1+ \town or \vassal
		\end{itemize}

		\subsubsection*{Vassalization}
		\begin{itemize}
			{
				\color{peaceReqColor}
				\item \strong{Requirements}
				\begin{itemize}
					\item Partial or Total Victory to Enforce
					\item Loser must be an NPR
					\item Victor must Occupy Loser's Capital
					\item Victor must Occup. 1+ Loser's \emph{de jure} Prov. in non-Cap. Area (if any)
				\end{itemize}
			}
			\item With \strong{Active Allies} (p.~30)
			\begin{itemize}
				\item Only apply for Realms for which the Victor satisfies all requirements
				\item For other Realms, treat as White Peace without \prestige loss
			\end{itemize}
			\item Loser becomes a Vassal of the Victor
			\item Victor places \vassalprovinces on all Loser's \emph{de jure} Prov., except Prov. Occup. by other PRs
			\item Victor may place 2 \influence in Loser's Realm
			\item Add \unrest to all Provinces gained in Areas where the Victor Occupied no Provinces
			\item Remove all Loser's \alliances/\marriages
			\item Victor may discard \claim from Area(s) of gained \vassalprovinces to remove 2 \unrest from same Area(s)
			\item Remove War/Truce tokens from the Loser
		\end{itemize}

		\subsubsection*{Force Conversion}
		\begin{itemize}
			{
				\color{peaceReqColor}
				\item \strong{Requirements}
				\begin{itemize}
					\item Partial or Total Victory to Enforce
					\item Victor must Control all Provinces in Loser's Capital Area
					\item Victor's Religion differs from Loser's
				\end{itemize}
			}
			\item With \strong{Active Allies} (p.~30)
			\begin{itemize}
				\item Only apply for Realms for which the Victor satisfies all requirements
				\item For other Realms, treat as White Peace without \prestige loss
			\end{itemize}
			\item Loser must change State Religion and Rel. of Capit. Area to State Rel. of Victor
			\item All Occupied Provinces must be returned
			\item Victor gains \p3
			\item Victor may add 2 \influence in Loser's Cap. Area
			\item Loser loses \p5
			\item Loser must remove 4 \influence
		\end{itemize}

		\subsubsection*{Humiliation}
		\begin{itemize}
			{
				\color{peaceReqColor}
				\item \strong{Requirements}
				\begin{itemize}
					\item Partial or Total Victory to Enforce
					\item Victor must Occupy Loser's Capital \conj{or} Loser must have Surrendered
					\item Loser may not be an NPR
				\end{itemize}
			}
			\item All Occup. Provinces must be returned
			\item Victor scores \prestige = 2× Tax Value of Provinces returned to Loser (max 10)
			\begin{itemize}
				\item No \prestige from Prov. of Active Allies
			\end{itemize}
			\item Loser loses the same amount of \prestige
		\end{itemize}

		\subsubsection*{Full Annexation}
		\begin{itemize}
			{
				\color{peaceReqColor}
				\item \strong{Requirements}
				\begin{itemize}
					\item Total Victory to Enforce
					\item Loser must be an NPR or Bot
				\end{itemize}
			}
			\item With \strong{Active Allies} only possible when resolved separately (p.~30)
			\item Remove all Loser's \alliances/\marriages
			\item If Loser is \activeally, the Allied PR loses \p2
			\item Victor may discard \claims in Area(s) of gained Prov. to remove 2 \unrest from same Area(s)
			\item If Emp. enforces Full Annex. on Subject with the same State Religion, drop \authority by 1 (p.~45)
		\end{itemize}

		\subsubsection*{Secure Desired Succession}
		\begin{itemize}
			{
				\color{peaceReqColor}
				\item \strong{Requirements}
				\begin{itemize}
					\item Partial or Total Victory to Enforce
					\item Loser's Capital must have a \disputedsuccession
					\item Victor must Occupy Loser's Capital
					\item Ignore Loser's Active Ally status
				\end{itemize}
			}
			\item All Occupied Prov. must be returned
			\item If Loser is NPR, all their other Wars end on White Peace terms
			\item Remove all \marriage/\disputedsuccession and \alliance/\activeally, except Victor's, from the Loser
			\item Victor scores \p3 per \marriage/\disputedsuccession removed
			\item PRs whose \marriage/\disputedsuccession was removed, lose \p3
			\item If Victor has \disputedsuccession on Loser, they
			\begin{itemize}
				\item Flip their \disputedsuccession back to \marriage
				\item Score \prestige = Loser's Tax Inc. (max 5)
			\end{itemize}
			\item Victor may
			\begin{itemize}
				\item If Loser is an NPR, add 4 \influence to Loser's Capital Area
				\item If Loser is a PR, replace Loser's Ruler with a Leader from any discard pile
				\item May then gain \alliance with the Loser
			\end{itemize}
		\end{itemize}

		\subsubsection*{Negotiated Peace}
		\begin{itemize}
			{
				\color{peaceReqColor}
				\item \strong{Requirements}
				\begin{itemize}
					\item Not Enforceable
					\item Both sides must be human players
				\end{itemize}
			}
			\item May agree who is Vict./Loser (if anyone)
			\item May agree on another listed Peace Term, but other conditions must be met
			\item If agreeing on Keep Current Board State 
			\begin{itemize}
				\item Both sides may exchange Occupied Provinces for \ducats
				\item Both sides may Liberate Provinces (with no \prestige gained)
			\end{itemize}
			\item In addition, may agree on one side taking an immediate \action{Cut Ties} and/or \action{P‑to‑P Diplomacy} (normal cost), disregarding restrictions for being at War
		\end{itemize}
	\end{multicols}
\end{eubox}\end{dynamiccontents*}

\begin{dynamiccontents*}{frameArrowsPageTwo}
	% Must be before the page ends but after all \zsavepos in other dynamic frames
	\begin{tikzpicture}
	\useasboundingbox (0,0) rectangle (\paperwidth,\paperheight);

	% Peace Resolution arrows (continues from previous page)
	\newlength{\peaceTermsStartYContinue} \setlength{\peaceTermsStartYContinue}{\calc{\zposy{arrowPeaceTermsStart}sp + \arrowAdjustYAfterSubsub}}
	\newlength{\peaceTermsEndY} \setlength{\peaceTermsEndY}{\calc{\zposy{arrowPeaceTermsEnd}sp + \arrowAdjustYBeforeSubsub}}
	\newlength{\peaceTermsEndX} \setlength{\peaceTermsEndX}{\zposx{arrowPeaceTermsEnd}sp}
	\newlength{\peaceTermsTurnX} \setlength{\peaceTermsTurnX}{\arrowXVerticalLeft}

	\drawArrow{(0mm, \peaceTermsStartYContinue) -- (\peaceTermsTurnX,\peaceTermsStartYContinue) -- (\peaceTermsTurnX,\peaceTermsEndY) -- (\peaceTermsEndX,\peaceTermsEndY)}

	\end{tikzpicture}
\end{dynamiccontents*}

\framebreak % Forcing frame break due to getting some weird errors after adding color to subsections (looks like some broken interaction between flowfram and other packages)
\subsection*{4. Income and Upkeep}
\begin{itemize}
	\item May \action{Take Loans} during this phase
\end{itemize}

\subsubsection*{A. Cut costs}
\begin{itemize}
	\item May (must if needed to avoid Bankrupt.):
	\begin{itemize}
		\item Fire Advisors
		\item Disband Units
		\begin{itemize}
			\item Regular Units ^^^^2192 Available \manpower
		\end{itemize}
		\item Recall Ships at sea
		\begin{itemize}
			\item Move to Ports in range via\\ non-Hostile Sea Zones (no \milpower cost)
		\end{itemize}
	\end{itemize}
\end{itemize}

\subsubsection*{B. Collect Income minus Costs}

\begin{tabularx}{\columnwidth}{ | X | X | }
\hline
\rowcolor{tblbgTax} + Base and Vassal Tax Income & Do not count slots with \cubes (p.~28) \\ \hline
\rowcolor{tblbgCost} - Advisor Upkeep & Papal Controller pays 1\ducat less per Advisor \\ \hline
\rowcolor{tblbgCost} - Military Maintenance & {
1\ducat per Regular Unit \newline
2\ducats per Mercenary \newline
½\ducat per Ship at sea
} \\ \hline
\rowcolor{tblbgCost} - Plague & ½\ducat per Tax Income in \plague Areas (r. up)\\ \hline
\rowcolor{tblbgCost} - Interest on Loans & 1\ducat per \interest \\ \hline
\rowcolor{tblbgStab} +/- \stability Modifier & \\ \hline
\rowcolor{tblbgExtra} + Emperor's \authority & \ducats = \authority \\ \hline
\rowcolor{tblbgExtra} + Income from Ideas & \\ \hline
\end{tabularx}

\subsubsection*{C. Corruption}
\begin{itemize}
	\item May discard \ducats to avoid costs
	\item 0-49 \ducats: No cost
	\item 50-59 \ducats: Pay 1\adminpower, gain \interest per unpaid \adminpower
	\item 60-69 \ducats: Pay 2\adminpower, gain \interest per unpaid \adminpower
	\item ...
\end{itemize}

\subsubsection*{D. Collect Monarch Power}
\begin{itemize}
	\item Gain \adminpower/\diplopower/\milpower = Ruler's + Advisor's Skill
	{\botrules
	\item Bots discard all spent \botpower (p.~3)
	\item Bots gain 6/7/8/9 \botpower
	\item If Bot has 20+ Small \towns, receives +1\botpower
	\item If Bot has 8 Large \towns, receives +1\botpower
	}
	\item If +3\stability, receive +2\monarchpower of any type
	\item If -3\stability, receive -1\monarchpower of any type
	\item Papal Controller receives +1\diplopower~\botrule{(or \botpower)}
	\item If Emperor is NPR (p.~45) \botrule{or Bot (p.~3)}
	\begin{itemize}
		\item Roll a 6-sided die
		\begin{itemize}
			\item If 6 \conj{or} ≥ curr. \authority + 2, raise \authority by 1
			\item If 1 \conj{or} ≤ curr. \authority~- 2, drop \authority by 1
		\end{itemize}
	\end{itemize}
	\item Emp. receives extra \monarchpower~\botrule{(or \botpower)} (p.~43):
	\begin{itemize}
		\item \authority = 2 or 3: Receive +1\diplopower
		\item \authority = 4 or 5: Receive +1\diplopower and +1\milpower
		\item \authority = 6 – Receive +2\diplopower and +1\milpower
	\end{itemize}
  \item Additional \monarchpower from Gov. Form Ideas
\end{itemize}

\subsubsection*{E. Score Prestige}
\begin{itemize}
	\item Uncontested Papal Controller scores \prestige = \# of Catholic PRs - 1 (max 3)
	\item If \authority = 6, Emperor scores \p1
	\item PRs with \idea{Abs. Mon.} and \stability>0, score \p1
	\item Active Crusades\zsavepos{arrowCrusadeStart}
	\item Active Power Struggle\zsavepos{arrowPowerStruggleStart}
	\item Remove Crusade/Excom. and \battlegroundarea tokens
\end{itemize}
\begin{dynamiccontents*}{frameCrusade}\begin{eubox}{\fhCrusade}
	\subsubsection*{\zsavepos{arrowCrusadeEnd}Crusade Scoring \normal{(p.~46)}}
	\begin{itemize}
		\item Catholic Realms \emph{Committed to Crusade}
		\begin{itemize}
			\item Score \p2 if target Area
			\begin{itemize}
				\item Contains their Units, \conj{and}
				\item Has no Provinces Owned by Muslim Realms
			\end{itemize}
			\item Lose 2 otherwise
		\end{itemize}
		\item If no Realm is \emph{Committed to Crusade}
		\begin{itemize}
			\item Papal Controller loses \p2
		\end{itemize}
	\end{itemize}
\end{eubox}\end{dynamiccontents*}
\begin{dynamiccontents*}{framePowerStruggle}\begin{eubox}{\fhPowerStruggle}
	\subsubsection*{\zsavepos{arrowPowerStruggleEnd}Scoring Power Struggles \normal{(p.~43)}}
	\begin{itemize}
		\item For each Battleground Area, score
		\begin{itemize}
			\item \p1 per Tax Value of Provinces Controlled (\vassals count as half)
			\item \p1 for being the only PR with \towns/\vassals there (only on the Main Map)
			\item \p1 for at least 1 \alliance/\marriage there
		\end{itemize}
		\item Additional criteria on the card
		\item Discard the card
	\end{itemize}
\end{eubox}\end{dynamiccontents*}

\subsection*{5. Clean-up}
\subsubsection*{A. Update and Refresh}
\begin{itemize}
	\item Allied Units in Armies ^^^^2192 Available \manpower
	\item \hspacezero\zsavepos{arrowManpowerStart}Update Manpower
	\item Refresh ½ Exhausted Units (min 3, max 6)
	\item Repair Heavy Ships in Port
	\item Refresh Merchants
	\item Add \colonists = \# of Colonial \claims (max 4)
	\item \botrule{Discard Bot \colonists if there is no vacant Territory (p.~3)}
	\item Remove \cube from \emph{Changed Nat. Focus} slot
\end{itemize}
\begin{dynamiccontents*}{frameManpower}\begin{eubox}{\fhManpower}
	\subsubsection*{Manpower \normal{(p.~23)}\zsavepos{arrowManpowerEnd}}
	\begin{itemize}
		\item Indicated by Town/Vassal Tracks and +1\manpower tokens
		\item Emperor has additional \manpower = \authority (p.~43)
		\item Max 20, \botrule{Bots have min 3 (p.~3)}
		\item When increases, add to Available \manpower
		\item When decreases
		\begin{itemize}
			\item Remove from Depl., Exh. or Avail. \manpower
			\item \botrule{Bots remove from Reserve first (p.~3)}
		\end{itemize}
	\end{itemize}
\end{eubox}\end{dynamiccontents*}

\subsubsection*{B. Board and Status Mat clean-up}
\begin{itemize}
	\item Remove \alliances
	\begin{itemize}
		\item \botrule{Between Bots and PRs (p.~3)}
		\item From DNPRs with Tax Income ≥ 10\ducats
	\end{itemize}
	\item Remove all \plague from Map
	\item \hspacezero\zsavepos{arrowImpInfluenceStart}Adjust Imperial \influence and redistribute
	\item If Emperor is at Peace
	\begin{itemize}
		\item Remove Imperial \manpower
		\item Remove Tag from \emph{Defending the HRE}
	\end{itemize}
	\item Remove Tags from \emph{Committed to Crusade}
	\item \hspacezero\zsavepos{arrowHreReligionStart}If Age III or IV, check HRE Religion (advanced rules) (p.~45)
	\item PR 1st to Pass gets the First Player token
	\begin{itemize}
		\item If already has it, PR 2nd to Pass gets it
	\end{itemize}
	\item \hspacezero\zsavepos{arrowBotDeckStart}\botrule{Reshuffle Bot decks (p.~3)}
\end{itemize}
\begin{dynamiccontents*}{frameImpInfluence}\begin{eubox}{\fhImpInfluence}
	\subsubsection*{Imperial Influence \normal{(p.~44)}\zsavepos{arrowImpInfluenceEnd}}
	\begin{itemize}
		\item \# of Imperial \influence = \authority
		\item Must be placed in HRE Areas with 1+ Prov. Owned by NPR HRE Members
		{\botrules
		\item Bot priorities (tie breakers: 1. Areas with Bot's \allies; 2. \az) (p.~3)
		\begin{itemize}
			\item Elec. Area where it would take least \influence to have more \influence than any other PR
			\item Any Elector Area not full
			\item Any HRE Area not full
		\end{itemize}
		}
	\end{itemize}
\end{eubox}\end{dynamiccontents*}
\begin{dynamiccontents*}{frameHreReligion}\begin{eubox}{\fhHreReligion}
	\subsubsection*{HRE Religion \normal{(p.~45)}\zsavepos{arrowHreReligionEnd}}
	\begin{itemize}
		\item If all Elector Areas are Protestant but HRE Religion is not
		\begin{itemize}
			\item HRE Religion becomes Protestant
			\item \authority drops by 1
		\end{itemize}
		\item If all Elector Areas are Catholic
		\begin{itemize}
			\item HRE Religion becomes Catholic
		\end{itemize}
		\item If Elector Areas have different Religions
		\begin{itemize}
			\item HRE has no official Religion (mark with Diverse Faiths token)
		\end{itemize}
	\end{itemize}
\end{eubox}\end{dynamiccontents*}
\begin{dynamiccontents*}{frameBotDeck}\begin{eubox}[botrulescolor]{\fhBotDeck}
	\botrules
	\subsubsection*{Reshuffling Bot Deck \normal{(p.~3)}\zsavepos{arrowBotDeckEnd}}
	\begin{itemize}
		\item EVENT is always reshuffled
		\item IDEA is always reshuffled
		\item Cards used for FOCUS are not reshuffled
		\item Half of the rest is reshuffled
	\end{itemize}
\end{eubox}\end{dynamiccontents*}

\subsubsection*{C. Discard down to 5 Action Cards}

\subsubsection*{D. End of Age Routine}
\begin{itemize}
	\item Skip if not end of Age \conj{or} Final Scoring triggered\zsavepos{arrowFinalStart}
	\item Place the Event deck for the next Age
	\item Replace all Milestones
	\item Replace unresearch. non-Basic Ideas
	\item The player with least \prestige (no ties) may replace 1 new Milestone or Idea
	\item Players with 1+ \marriage score \p1
	\begin{itemize}
		\item Then in turn order
		\begin{itemize}
			\item Rem. 1\marriage (prefer NPR) or pay 2\diplopower
			\item \botrule{Bots do not remove \marriages (p.~3)}
			\end{itemize}
	\end{itemize}
	\item \botrule{Reset Bot decks (p. 3)}
\end{itemize}

\subsection*{Final Scoring}
\begin{itemize}
	\item Trigger Final Scoring \strong{after Phase 5} if\zsavepos{arrowFinalEnd}
	\begin{itemize}
		\item No more Events left, \conj{or}
		\item PR has ≥100 \prestige and lead of ≥20 \prestige, \conj{or}
		\item PR has all \towns and \vassals on the Map
	\end{itemize}
	\item Score Missions from hand (no effects)
	\item Score \prestige = Base and Vassal Tax Income
	\item Score \p1 per \core, \p1 per \marriage, \p2 per \alliance
	\item Papal Contr. scores \prestige = \# of Cath. PRs
	\item Emperor scores \prestige = \authority
	\item Score \prestige = 2× \stability
	\item Subtract \p1 per Tax Value of Occup. \towns
	\item Subtract \p1 per \interest
	\item PR with most \prestige wins, tie breakers: 1.~most \monarchpower, 2.~most \ducats%
\end{itemize}

\begin{dynamiccontents*}{frameArrowsPageThree}
	% Must be before the page ends
	\begin{tikzpicture}
		\useasboundingbox (0,0) rectangle (\paperwidth,\paperheight);

		% Manpower arrow
		\newlength{\manpowerStartY} \setlength{\manpowerStartY}{\calc{\zposy{arrowManpowerStart}sp + \arrowAdjustYList}}
		\newlength{\manpowerStartX} \setlength{\manpowerStartX}{\calc{\zposx{arrowManpowerStart}sp + \arrowAdjustXBeforeList}}
		\newlength{\manpowerEndY} \setlength{\manpowerEndY}{\calc{\zposy{arrowManpowerEnd}sp + \arrowAdjustYAfterSubsub}}
		\newlength{\manpowerEndX} \setlength{\manpowerEndX}{\calc{\zposx{arrowManpowerEnd}sp + \arrowToTextSpacing}}
		\newlength{\manpowerTurnX} \setlength{\manpowerTurnX}{\arrowXVerticalMidRight}

		\drawArrow{(\manpowerStartX, \manpowerStartY) -- (\manpowerTurnX,\manpowerStartY) -- (\manpowerTurnX,\manpowerEndY) -- (\manpowerEndX,\manpowerEndY)}

		% Imperial Influence arrow
		\newlength{\impinfStartY} \setlength{\impinfStartY}{\calc{\zposy{arrowImpInfluenceStart}sp + \arrowAdjustYList}}
		\newlength{\impinfStartX} \setlength{\impinfStartX}{\calc{\zposx{arrowImpInfluenceStart}sp + \arrowAdjustXBeforeList}}
		\newlength{\impinfEndY} \setlength{\impinfEndY}{\calc{\zposy{arrowImpInfluenceEnd}sp + \arrowAdjustYAfterSubsub}}
		\newlength{\impinfEndX} \setlength{\impinfEndX}{\calc{\zposx{arrowImpInfluenceEnd}sp + \arrowToTextSpacing}}
		\newlength{\impinfTurnX} \setlength{\impinfTurnX}{\arrowXVerticalMidRight}

		\drawArrow{(\impinfStartX, \impinfStartY) -- (\impinfTurnX,\impinfStartY) -- (\impinfTurnX,\impinfEndY) -- (\impinfEndX,\impinfEndY)}

		% HRE Religion arrow
		\newlength{\hreStartY} \setlength{\hreStartY}{\calc{\zposy{arrowHreReligionStart}sp + \arrowAdjustYList}}
		\newlength{\hreStartX} \setlength{\hreStartX}{\calc{\zposx{arrowHreReligionStart}sp + \arrowAdjustXBeforeList}}
		\newlength{\hreEndY} \setlength{\hreEndY}{\calc{\zposy{arrowHreReligionEnd}sp + \arrowAdjustYAfterSubsub}}
		\newlength{\hreEndX} \setlength{\hreEndX}{\calc{\zposx{arrowHreReligionEnd}sp + \arrowToTextSpacing}}
		\newlength{\hreTurnX} \setlength{\hreTurnX}{\arrowXVerticalMidRight}

		\drawArrow{(\hreStartX, \hreStartY) -- (\hreTurnX,\hreStartY) -- (\hreTurnX,\hreEndY) -- (\hreEndX,\hreEndY)}

		% Bot Deck arrow
		\newlength{\botDeckStartY} \setlength{\botDeckStartY}{\calc{\zposy{arrowBotDeckStart}sp + \arrowAdjustYList}}
		\newlength{\botDeckStartX} \setlength{\botDeckStartX}{\calc{\zposx{arrowBotDeckStart}sp + \arrowAdjustXBeforeList}}
		\newlength{\botDeckEndY} \setlength{\botDeckEndY}{\calc{\zposy{arrowBotDeckEnd}sp + \arrowAdjustYAfterSubsub}}
		\newlength{\botDeckEndX} \setlength{\botDeckEndX}{\calc{\zposx{arrowBotDeckEnd}sp + \arrowToTextSpacing}}
		\newlength{\botDeckTurnX} \setlength{\botDeckTurnX}{\arrowXVerticalMidRight}

		\drawArrow{(\botDeckStartX, \botDeckStartY) -- (\botDeckTurnX,\botDeckStartY) -- (\botDeckTurnX,\botDeckEndY) -- (\botDeckEndX,\botDeckEndY)}

		% Crusade Scoring arrow
		\newlength{\crusadeStartY} \setlength{\crusadeStartY}{\calc{\zposy{arrowCrusadeStart}sp + \arrowAdjustYAfterSubsub}}
		\newlength{\crusadeStartX} \setlength{\crusadeStartX}{\calc{\zposx{arrowCrusadeStart}sp + \arrowToTextSpacing}}
		\newlength{\crusadeEndY} \setlength{\crusadeEndY}{\calc{\zposy{arrowCrusadeEnd}sp + \arrowAdjustYBeforeSubsub}}
		\newlength{\crusadeEndX} \setlength{\crusadeEndX}{\zposx{arrowCrusadeEnd}sp}
		\newlength{\crusadeTurnX} \setlength{\crusadeTurnX}{\calc{\arrowXVerticalMidLeft - 1mm}}

		\drawArrow{(\crusadeStartX, \crusadeStartY) -- (\crusadeTurnX,\crusadeStartY) -- (\crusadeTurnX,\crusadeEndY) -- (\crusadeEndX,\crusadeEndY)}

		% Power Struggles arrow
		\newlength{\powerStartY} \setlength{\powerStartY}{\calc{\zposy{arrowPowerStruggleStart}sp + \arrowAdjustYAfterSubsub}}
		\newlength{\powerStartX} \setlength{\powerStartX}{\calc{\zposx{arrowPowerStruggleStart}sp + \arrowToTextSpacing}}
		\newlength{\powerEndY} \setlength{\powerEndY}{\calc{\zposy{arrowPowerStruggleEnd}sp + \arrowAdjustYBeforeSubsub}}
		\newlength{\powerEndX} \setlength{\powerEndX}{\zposx{arrowPowerStruggleEnd}sp}
		\newlength{\powerTurnX} \setlength{\powerTurnX}{\arrowXVerticalMidLeft}

		\drawArrow{(\powerStartX, \powerStartY) -- (\powerTurnX,\powerStartY) -- (\powerTurnX,\powerEndY) -- (\powerEndX,\powerEndY)}

		% Final Scoring arrow
		\newlength{\finalStartY} \setlength{\finalStartY}{\calc{\zposy{arrowFinalStart}sp + \arrowAdjustYText}}
		\newlength{\finalStartX} \setlength{\finalStartX}{\calc{\zposx{arrowFinalStart}sp + \arrowToTextSpacing}}
		\newlength{\finalEndY} \setlength{\finalEndY}{\calc{\zposy{arrowFinalEnd}sp + \arrowAdjustYText}}
		\newlength{\finalEndX} \setlength{\finalEndX}{\calc{\zposx{arrowFinalEnd}sp + \arrowToTextSpacing}}
		\newlength{\finalTurnX} \setlength{\finalTurnX}{\arrowXVerticalRight}

		\drawArrow{(\finalStartX, \finalStartY) -- (\finalTurnX,\finalStartY) -- (\finalTurnX,\finalEndY) -- (\finalEndX,\finalEndY)}
		
	\end{tikzpicture}
\end{dynamiccontents*}

\end{document}
